### 2018-10-23 Sections/physical_architectures_for_quantum_computing.tex
More editing

A quantum computer will be made up of several superconducting qubits and a quantum operation will mostly involve more than one qubit. Hence it is essential to find ways to transfer the information from one set of superconducting qubits to another. While transferring the information we need to keep in mind that its quantum nature should be preserved. This essentially means we need to find a different kind of qubit which can carry information from one place to another and interacts weakly with the other qubits and the environment. It is well known that photons can move from one place to another and they interact very weakly with each other and the environment. They can be made into qubit systems by using their horizontal and vertical polarisation degrees of freedom as two levels of the system. The photonic qubits useful to carry information should have frequency which is equal to the energy difference between the qubit levels. For a superconducting qubit the energy difference is very small and hence the frequency of the optical qubits will correspond to microwaves whose wavelength lies in the range from 100$\mu$m and 1m.

The information transfer between the different superconducting qubits is achieved using a resonator which acts as a quantum data bus. A simple resonator is an LC circuit which can support only one frequency mode, but a waveguide resonator can support multiple modes. In general the transmission line circuits used in the quantum non-linear electric circuits are in the form of coplanar waveguides. These waveguides are engineered to handle a particular set of frequencies and it is also to produce transmission lines of tuneable frequencies. The tuneable resonators are very important in quantum optics and are useful in implementing controllable coupling between different quantum elements and also in shaping the wave packets of photons.

In cavity quantum electrodynamics the interaction of a natural atom with an optical photon in the visible wavelength is studied. Similarly, the interaction between the quantum non-linear electrical circuit and the microwave photon is investigated in circuit quantum electrodynamics. The coupling strength between a natural atom and visible light photon is fixed and an atom couples weakly with the photon \cite{bib:raimond2001manipulating}. Meanwhile the coupling strength between a superconducting qubit and microwave can be changed by engineering the parameters of the qubit and resonator and we can have strong and ultra strong coupling between the qubit and the photons \cite{bib:wallraff2004strong}. Further the coupling between the atom and the photon can be tuned during the course of an experiment. Several quantum optics components like mirrors, beamsplitters, circulators and switches can also be designed based on the quantum electric circuits.

>>>>

To build a scalable quantum computer, multiple qubits are required. Hence, it is essential to find ways to transfer quantum information between distinct superconducting qubits. When doing so, it is essential that quantum coherence be preserved. This implies we need to find a different kind of qubit, which can carry information from one place to another, but interacts only weakly with the other qubits and the environment. Photons are the ideal candidate for this (Sec.~\ref{sec:optical_encoding}). Photonic qubits for carrying information should have frequencies equal to the energy difference between qubit levels. For a superconducting qubit, the energy difference is very small and hence the frequency of optical qubits will correspond to microwaves whose wavelength lies in the range 100$\mu$m-1m.

Information transfer between distinct superconducting qubits is achieved using a resonator, which acts as a quantum data bus. A simple resonator is an LC circuit, which can support only one frequency mode, but a waveguide resonator can support multiple modes. In general, the transmission line circuits used in non-linear quantum electric circuits are in the form of coplanar waveguides. These waveguides are engineered to handle a particular set of frequencies, and to produce transmission lines with tuneable frequency. Tuneable resonators are very important in quantum optics, and are useful in implementing controllable coupling between different quantum elements and also in shaping the wave-packets of photons.

In cavity quantum electrodynamics (QED) the interaction of a natural atom with an optical photon in the visible wavelength is considered. Similarly, the interaction between quantum non-linear electrical circuits and  microwave photons are investigated in circuit QED. The coupling strength between a natural atom and visible light photon is fixed, where atoms couple weakly with photons \cite{bib:raimond2001manipulating}. Meanwhile, the coupling-strength between a superconducting qubit and microwave can be changed by engineering the parameters of the qubit and resonator, yielding strong and ultra-strong coupling between qubits and photons \cite{bib:wallraff2004strong}. Furthermore, the coupling between an atom and a photon can be tuned during the course of an experiment. Several quantum optics components such as mirrors, beamsplitters, circulators and switches can also be designed based on quantum electric circuits.
